### 2024-03-03 docs/manuscript/manuscript.qmd
Reordenando ubicacion de archivos
Codigo junto a su resultado (figura)

```{r tbl-1}
#| echo: false
#| message: false
#| warning: false
readRDS(file = "tables/tbl-descriptives.RDS") |> 
  font(part = "all", fontname = "Times")
```
**Table 1**. Main sample characteristics. Body composition and sociodemograpic variables are displayed for the overall sample and aggregated by sex. Differences between males and females are displayed as SMD and CI~95%~ for continuous variables.

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
readRDS(file = "tables/tbl-descriptives.RDS") |> 
  font(part = "all", fontname = "Times")
```
**Table 1**. Main sample characteristics. Body composition and sociodemograpic variables are displayed for the overall sample and aggregated by sex. Differences between males and females are displayed as SMD and CI~95%~ for continuous variables.
